A New Metric for the Analysis of Swarms using Potential Fields

### 2018-10-16 paper.tex
Updates 16-10-2018

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/kenda}}]{David Kendall}
has been a Senior Lecturer in Computing at Northumbria University since 1989, except for a brief period as a Lecturer in Computer Science at Durham University (2001-02). Previously, he was a Research Associate at Newcastle University (1987-89), following experience as a Senior Software Engineer in industry (1983-86). He has an M.A. degree in Literae Humaniores from Oxford University, where he studied at New College. He received M.Sc. and Ph.D. degrees in Computing Science from Newcastle University. His research interests are in the area of formal modelling and analysis of embedded systems. 
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/kenda}}]{David Kendall}
received the M.A. degree in literae humaniores from New College, Oxford University, and the M.Sc. and Ph.D. degrees in computing science from Newcastle University. He was a Research Associate at Newcastle University from 1987 to 1989, following experience as a Senior Software Engineer in industry from 1983 to 1986. He has been a Senior Lecturer in computing at Northumbria University since 1989, except for a brief period as a Lecturer in computer science at Durham University from 2001 to 2002. His research interests are in the areas of formal methods, embedded systems, distributed systems, security, and privacy.
\end{IEEEbiography}
